SPARQL on the open, decentralised Web

### 2016-06-05 dissertation/problems.tex
make todos visible
TPF problem on microcontroller

@@

\begin{problem}\label{prob:useexist}
How can the adoption of existing vocabularies be encouraged? 
% TODO: Find the ref by Frank on the economics
\end{problem}

@@

Finally, the intention was to bring convergence to the topics of this
thesis around a system to cache results that could be reused in
subsequent queries. As noted in Section~\ref{sec:motivcache}, this was
motivated by opportunity as well as problems, but it is intended to
address
problems~\ref{prob:syntacticcache}~and~\ref{prob:cachecartesian}. In
addition, problems~\ref{prob:zipf}~and~\ref{prob:uniform} are
compounded by Problem~\ref{prob:nostats}, but alleviated somewhat by
the presence of cardinality estimates given by Triple Pattern
Fragments, which we exploit.

@@

I have not approached any of the problems of
Section~\ref{sec:semproblems}, mainly because I think it is an open
question which of these approaches will be adopted in practice, and
whatever the solution may be, their designers should make sure they
are orthogonal to the other problems discussed here. Thus, it was
natural to consider them out of scope. 
% TODO: However, I shall assume that no inference is needed in the
% following examples.

@@

Problem~\ref{prob:tpf} was along with
problems~\ref{prob:sparqlcomplex},~\ref{prob:endpointunpred}~and~\ref{prob:syntacticcache}
part of the motivation of \cite{ldf1} and \cite{verborgh2014querying},
and this builds in part on the insight I contributed when addressing
Problem~\ref{prob:lapis}. Their solution was to define an ontology to
describe an interface that can answer a single triple pattern, but
since it is hypermedia, it can be described in the messages of the
protocol.

>>>>

Heterogeneity should also be expected in different types of servers
and clients, in particular

\begin{problem}\label{prob:microcontroller}
A client running on a microcontroller does not have significant
processing capability.
\end{problem}

@@

\begin{problem}\label{prob:useexist}
How can the adoption of existing vocabularies be encouraged? 
\todo{ Find the ref by Frank on the economics}
\end{problem}

@@

Finally, the intention was to bring convergence to the topics of this
thesis around a system to cache results that could be reused in
subsequent queries. As noted in Section~\ref{sec:motivcache}, this was
motivated by opportunity as well as problems, but it is intended to
address
problems~\ref{prob:syntacticcache}~and~\ref{prob:cachecartesian}.
Triple Pattern Fragments shifts most of the processing from servers to
clients, but Problem~\ref{prob:microcontrollers} makes that in some
cases infeasible.  In addition,
problems~\ref{prob:zipf}~and~\ref{prob:uniform} are compounded by
Problem~\ref{prob:nostats}, but alleviated somewhat by the presence of
cardinality estimates given by Triple Pattern Fragments, which we
exploit.

@@

I have not approached any of the problems of
Section~\ref{sec:semproblems}, mainly because I think it is an open
question which of these approaches will be adopted in practice, and
whatever the solution may be, their designers should make sure they
are orthogonal to the other problems discussed here. Thus, it was
natural to consider them out of scope. 
\todo{However, I shall assume that no inference is needed in the
following examples.}

@@

Problem~\ref{prob:tpf} was along with
problems~\ref{prob:sparqlcomplex},~\ref{prob:endpointunpred}~and~\ref{prob:syntacticcache}
part of the motivation of \cite{ldf1} and \cite{verborgh2014querying},
and this builds in part on the insight I contributed when addressing
Problem~\ref{prob:lapis}. Their solution was to define an ontology to
describe an interface that can answer a single triple pattern, but
since it is hypermedia, it can be described in the messages of the
protocol. However, the solution in \cite{verborgh2014querying} does
not take into account Problem~\ref{prob:microcontroller}, so query
planning that shifts the burden to a cost-model driven balance between
server, proxy and client is an interesting direction.
